Heuristics and Really Hard Instances for Subgraph Isomorphism Problems

### 2016-01-11 paper/paper.tex
Move

However, these algorithms cannot handle \emph{arbitrary} instances of this size. The experimental
evaluations of these algorithms were performed using a mix of real-world graphs, graphs that encode
biochemistry and computer vision problems, and randomly generated graph pairs. Using random
instances to evaluate algorithm behaviour can be beneficial, because it provides a way of generating
many instances cheaply, and reduces the risk of over-fitting when tuning design parameters. The
random instances used in each case came from common datasets (cite ??), which were generated by
taking a random subgraph of a random graph (using various models, including scale-free and bounded
degree) and permuting the vertices.  This is not ideal: such instances are guaranteed to be
satisfiable, and so existing benchmark suites contain relatively few non-trivial unsatisfiable
instances. These instances also tend to be computationally fairly easy, with most of the difficulty
being in dealing with the size of the model.

@@

?? \citep{Anton:2009}

>>>>

However, these algorithms cannot handle \emph{arbitrary} instances of this size. The experimental
evaluations of these algorithms were performed using a mix of real-world graphs, graphs that encode
biochemistry and computer vision problems, and randomly generated graph pairs. Using random
instances to evaluate algorithm behaviour can be beneficial, because it provides a way of generating
many instances cheaply, and reduces the risk of over-fitting when tuning design parameters. The
random instances used in each case came from common datasets (cite ??), which were generated by
taking a random subgraph of a random graph (using various models, including scale-free and bounded
degree) and permuting the vertices.  This is not ideal: such instances are guaranteed to be
satisfiable (?? mention \citep{Anton:2009}), and so existing benchmark suites contain relatively few
non-trivial unsatisfiable instances. These instances also tend to be computationally fairly easy,
with most of the difficulty being in dealing with the size of the model.

@@
